A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-18 doc/draft-01-stokes/03analysis.tex
update lemma and radiation condition
rename files

\begin{definition} \label{def:radcond}
Let $(\bu,p)$ satisfy the oscillatory Stokes equations in
the exterior of a bounded domain. We say that
the pair $(\bu,p)$ is {\em radiating} if
$p$ is bounded, $p \to 0$ as $r = |\xx| \to \infty$, and 
\begin{equation}
\lim_{r\to \infty} \sqrt{r} \left| \bt - i k \bu \right| \to 0 \, ,
\label{eq:radcond}
\end{equation}
uniformly in direction where $\bt = \bsigma \cdot \bnu$
with $\bnu = \xx/|\xx|$, i.e. $\bt$ is the surface
traction on $\partial B_r(0)$.     
\end{definition}

\begin{proposition}
The oscillatory Stokeslet, as in \eqref{eq:ostokeslet}, satisfies
the radiation condition in Definition \ref{def:radcond}.
Assuming that a density $\bmu$ is integrable and satisfies
$\int_\Gamma \bmu\cdot \bnu dS = 0$, where $\bnu$ denotes the
outward normal to the curve $\Gamma$, the oscillatory Stokes
double layer potential $\bD\bmu$, as in \eqref{eq:doublelayer},
also satisfies the radiation condition.
\end{proposition}

\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

@@

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lem}
  \label{lem:rellich}
    Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that $\bu$ satisfies the oscillatory Stokes equation in
  $E$ and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lem}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$ must be zero. 
Thus, 
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
for sufficiently large $r$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\end{proof}
\begin{remark} \label{rmk:harmu}
  Note that if $\bu$ satisfies the assumptions
  of~\cref{lem:rellich}, then each component is harmonic
  and thus $\bu$ satisfies
\begin{align}
k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
\nabla \cdot \bu &= 0 \, . \nonumber
\end{align}
Taking the inner product of~\cref{eq:massconsred} with $\nabla^{\perp}$,
we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
and $\nabla \cdot \bu = 0$, i.e. $u_1 - i u_2$ is analytic.
\end{remark}
\begin{remark}
Note that in Rellich's lemma $\bu$ need not be a radiating solution. 
All that is assumed of $\bu$ is that it satifies the PDE in $E$.
\end{remark}

@@

\begin{thm}
\label{thm:dlmain}
Suppose that $\Omega$ is a simply connected domain, then the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k$ is 
Dirichlet eigenvalue for Stokes equation on $\Omega$.
\end{thm}
\begin{proof}
Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-} = (\cI - 2\cD_{k}) \bmu = 0$ on $\Gamma$. 
Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again for the jump in surface traction
for the double layer potential, we conclude that the exterior limit
of the surface traction $\bt^{+} = 0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Sotkes equation in the exterior $E$.
From uniqueness of the Neumann problem in the exterior $E$, we conclude
that $\bu \equiv 0$ in $E$ as well, which in particular implies that
the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k$ is not a Dirichlet
eigenvalue for the Stokes equation on $\Omega$.

From Green's representation for the oscillatory Stokes qeuation, 
we know that 
  \begin{equation} \label{eq:rep-theorem}
    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
Suppose thatw $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
and let $\bu$ denote the corresponding eigenfunction, and let $\bt^{-}$ denote
the surface traction associated with the eigenfunction on the boundary $\Gamma$.
Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted to the boundary
$\bu^{-} = 0$. 
Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
\begin{equation}
\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, ,\implies \left(\cI - 2\cDt_{k} \right) 
\bt^{-} = 0 \, .
\end{equation}
From the Fredholm alternative, it then follows that $(\cI - 2\cD)$ has a non-trivial 
null-space.
However, we need to prove that $(\cI -2\cD - 2\cW)$ has a non-trivial null-space
for which we need the following two lemmas.

@@

\begin{lemma}
If $\bt^{-}$ is the surface traction associated with an interior Dirichlet
Stokes eigenfunction $\bu$, then $\bt^{-}$ and $\bnu$ are linearly independent.
\end{lemma}
\begin{proof}
We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
This follows from the application of the divergence theorem and the fact that
oscillatory Stokeslet is divergence free in $\Omega$. 
If $\bt^{-}$ is a surface traction associated with a Stokes eigenvalue, then
using Green's theorem, it follows that
$\bS_{k}[\bt^{-}](\bx) = u(\bx) \neq 0$ for $\bx \in \Omega$ and
thus $\bt^{-}$ and $\bnu$ are linearly independent.
\end{proof}

We now turn to the proof of the main result of the section.
We know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt)$ are two linearly independent
vectors in the null space.
Let $c = \left< \bt^{-},\bnu \right>$. Then, it follows that 
$\left<\bt^{-} -c \bnu, \bnu \right> = 0$ and thus
$\cW[\bt^{-} - c\bnu] = 0$. 
Since $\bt^{-}$ and $\bnu$ are linearly independent, we note that
$\bt^{-} -c\bnu \neq 0$.
Combining these results, we get that
$(\cI - 2\cDt_{k} - 2\cW) (\bt^{-} - c\bnu) = 0$. 
Since $\bt^{-}-c\bnu$ is non-trivial, and $\cW$ is self-adjoint, 
it follows from the Fredholm alternative
that the operator $\cI - 2\cD_{k} - 2\cW$ is also not invertible.
\end{proof}

@@

@@

As noted in~\cite{zhao2015robust}, this lack of one-to-one correspondance between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains causes non-robustness and introduces near 
resonanaces for simply connected domains
which are almost multiply connected. 
This issues is discussed in detail
in example~\cref{sec:numanalysis-nearly-mult-con}.

\subsubsection{Mixed layer potential representation}
\label{subsec:mixedanalysis}
The non-robustness of the double layer potential representation
for computing the Dirichlet eigenvalues of Stokes equation can be remdied
by the standard approach of using the mixed layer potential representation,
i.e. setting
$\bu = (\bD + i\eta \bS)
\bmu$, 
where $\bmu$ is the unknown density to be solved for, and $\eta \in \mathbb{R}^{+}$ 
On imposing the boundary conditions and using~\cref{lem:jump-conds}, 
we obtain the following integral equation on the boundary 
\begin{equation}
(\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \, . 
\end{equation}
As noted in~\cref{subsubsec:nullspacecorr}, this integral equation 
is also rank-deficient, and we instead use the following 
equivalent integral equation for $\bmu$,
\begin{equation}
(\cI - 2\cD_{k} -2i\eta \cS_{k}  -2\cW)\bmu = -2 \ff \, .
\end{equation}

We now prove that for any bounded region $\Omega$ (simply or multiply
connected) with $C^{2}$ boundaries, there exists a one-to-one correspondance
between the invertibility of the operator
$\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues
of the Stokes operator on $Omega$. 
The following theorem proves this result.

\begin{thm}
Suppose $\Omega$ is a bounded region defined by the intersection of a 
simply connected domain $\Omega_{0}$ and the exteriors of a finite collection
of bounded simply connected domains $\{ \Omega_{i} \}_{i=1}^{m}$.
As before let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$ and let
$\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
Then the operator $\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$
is invertible if and only if $k$ is not a Dirichlet eigenvalue
for the Stokes operator on $\Omega$.
\end{thm}

\begin{proof}
Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, , \label{eq:mlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2i\eta\cS_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:mlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k} - 2i\eta \cS_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD[\bmu] -2i\eta\bS[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-} = (\cI - 2\cD -2ik\cS) \bmu = 0$ on $\Gamma$. 
Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$.
Using~\cref{lem:jump-conds}  
we observe that the exterior limit 
of the surface traction is $\bt^{+} = i\eta \bmu(\xx)$
and the exterior limit of the velocity is 
$\bu^{+} = \bmu(\xx)$ on $\Gamma$.
\begin{remark}
Note that there is a slight abuse of notation here for the obstacle
boundaries, since the exterior limit with respect to $\Omega$ 
for the boundary $\Gamma_{j}$ is the traditional interior 
limit with respect to the obstacle region $\Omega_{j}$.
\end{remark}
We first show that $\bmu=0$ on $\Gamma_{0}$. 
To this end, note that $\bu$ is a radiating solution of the oscillatory
Sotkes equation in the exterior $E$.
From uniqueness of the impedance problem in the exterior $E$, we conclude
that $\bu \equiv 0$ in $E$ as well, which in particular implies that
the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma_{0}$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ \, on
$\Gamma_{0}$. 
To show that $\bmu=0$ on $\Gamma_{j}$, we observe that
$\bmu$ is also a solution to the oscillatory Stokes equation
in each of the obstacles $\Omega_{j}$ as well.
Applying Green's identity and using the fact that 
the interior limits with respect to $\Omega_{j}$ (see remark)
of the surface traction and the velocity
are $i\eta \bmu$ and $\bmu$ respectively, we get
\begin{equation}
\int_{\Omega_{j}} (|e(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
= \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
i\overline{\eta}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
\end{equation}
Taking the imaginary part of the above equation, we get
\begin{equation}
2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(\eta)
\int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
\end{equation}
This implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
Thus $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is invertible when $k$ 
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.

>>>>

\begin{definition} \label{def:radcond}
Let $(\bu,p)$ satisfy the oscillatory Stokes equations in
the exterior of a bounded domain. We say that
the pair $(\bu,p)$ is {\em radiating} if
\begin{equation}
\lim_{r\to \infty} \sqrt{r} \left| \bt - i k \bu \right| \to 0 \, ,
\label{eq:radcond}
\end{equation}
uniformly in direction where $\bt = \bsigma \cdot \bnu$
with $\bnu = \xx/|\xx|$, i.e. $\bt$ is the surface
traction on $\partial B_r(0)$.     
\end{definition}

\begin{thrm}
The oscillatory Stokeslet, as defined in \eqref{eq:ostokeslet}, 
satisfies the radiation condition in Definition \ref{def:radcond}.
Suppose that $\Gamma$ is the boundary of a region $\Omega$
and is $C^{2}$. 
Suppose that $\bmu \in C(\Gamma)$ and satsifies
$\int_{\Gamma} \bmu \cdot \bnu dS = 0$, where
$\bnu$ dentoes the outward normal to the curve $\Gamma$.
Then, the oscillatory Stokes 
double layer potential $\bD[\bmu]$, as defined in \eqref{eq:doublelayer},
also satisfies the radiation condition.
\end{thrm}

\begin{proof}
Consider the Stokeslet induced by an arbitrary charge
$k^2 \bpsi$ at the origin where $\psi \in \mathbb{C}^2$ 
is a constant. Let $r = |\xx|$,
$\bnu(\xx) = \xx/|\xx|$, and $\btau(\xx) = \bnu(\xx)^\perp$. We have

@@

\begin{cor}
  If $(\bu,p)$ is a radiating solution of
  the oscillatory Stokes equations, then
  $p$ is bounded and $p\to 0$ as $r\to\infty$.
\end{cor}

In the next lemma, we prove the analogue of Rellich's lemma for the
oscillatory Stokes equation. 
\begin{lem}
  \label{lem:rellich}
    Let the unbounded region $E$ be given as the exterior
  of a finite collection of bounded domains.
  Suppose that $\bu$ satisfies the oscillatory Stokes equation in
  $E$ and that 
\begin{equation}
\lim_{r \to \infty} \int_{|\by|=r} |\bu|^2 dS = 0 
\, . \label{eq:decayatinf}
\end{equation}
Then each component of $\bu$ is harmonic in $E$.
\end{lem}
\begin{proof}
We first note that each component of $\bu= (u_{1},u_{2})$ satisfies the 
oscillatory biharmonic equation in $E$, i.e.
\begin{equation}
\Delta (\Delta + k^2) u_{j} = 0 \quad j=1,2 \,. \nonumber
\end{equation}
For $r$ sufficiently large, we can express $u_{j}$ in the Fourier basis as
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} a_{j,n}(r) e^{i n \theta}  \quad 
j=1,2 \, . \nonumber
\end{equation}
Using Parseval's identity then
\begin{equation}
\int_{|\by|=r} |\bu|^2 dS = r\sum_{n=-\infty}^{\infty} |a_{1,n}(r)|^2  +
|a_{2,n}(r)|^2 \, . \nonumber
\end{equation}
Since $\bu$ satisfies~\cref{eq:decayatinf}, we conclude that
\begin{equation}
\lim_{r\to\infty} r|a_{j,n}(r)|^2 = 0 \quad j=1,2 \, , \label{eq:adecay}
\end{equation}
Since $u_{j}$, $j=1,2$ satisfies the oscillatory biharmonic equation,
the functions $a_{j,n}$ are linear combinations of 
\begin{equation}
r^{|n|}, r^{-|n|}, H^{1}_{n}(k r), H^{2}_{n}(k r) \, , \quad
n\neq 0 \, , \nonumber
\end{equation}
and
\begin{equation}
1, \log{(r)}, H^{1}_{0}(k r), H^{2}_{0}(k r) \quad n=0 \, ,  \nonumber
\end{equation} 
where $H_{n}^{1,2}(\cdot)$ are the Hankel functions of the first and
second kind of order $n$.
Since $a_{j,n}(r)$ satisfy~\cref{eq:adecay}, and using the asymptotic 
expansion of $H_{n}^{1,2}(r)$, we note that the projection of 
$a_{j,n}$ on $r^{|n|}$, and $H_{n}^{1,2}(k r)$ must be zero. 
Thus, 
\begin{equation}
u_{j}(r,\theta) = \sum_{n=-\infty}^{\infty} \frac{a_{j,n} e^{i n \theta}}{r^{|n|}} 
\, , \nonumber
\end{equation}
for sufficiently large $r$.
Finally, by \cref{cor:analytic}, $\bu$ is
analytic in $E$. Therefore, each $u_j$ is harmonic
throughout $E$.
\end{proof}
\begin{remark} \label{rmk:harmu}
  Note that if $\bu$ satisfies the assumptions
  of~\cref{lem:rellich}, then each component is harmonic
  and thus $\bu$ satisfies
\begin{align}
k^2 \bu &= \nabla p  \quad \label{eq:massconsred} \\
\nabla \cdot \bu &= 0 \, . \nonumber
\end{align}
Taking the inner product of~\cref{eq:massconsred} with $\nabla^{\perp}$,
we note that $\bu$ satisfies both $\nabla^{\perp} \cdot \bu = 0$ 
and $\nabla \cdot \bu = 0$, i.e. $u_1 - i u_2$ is analytic.
\end{remark}
\begin{remark}
Note that in~\cref{lem:rellich}, $\bu$ need not be a radiating solution. 
All that is assumed of $\bu$ is that it satifies the PDE in $E$.
\end{remark}

@@

\begin{thrm}
\label{thm:dlmain}
Suppose that $\Omega$ is a simply connected domain, then the operator
$(\cI - 2\cD_{k} - 2 \cW)$ is not invertible if and only if $k$ is 
Dirichlet eigenvalue for Stokes equation on $\Omega$.
\end{thrm}
\begin{proof}
Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} - 2\cW) \bmu = 0 \, , \label{eq:dlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:dlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:dlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-} = (\cI - 2\cD_{k}) \bmu = 0$ on $\Gamma$. 
Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$. 
Using~\cref{lem:jump-conds} again for the jump in surface traction
for the double layer potential, we conclude that the exterior limit
of the surface traction $\bt^{+} = 0$ on $\Gamma$. 
Note that $\bu$ is a radiating solution of the oscillatory
Sotkes equation in the exterior $E$, since
$\cW[\mu] = 0$ implies $\int_{\Gamma} \mu \cdot \bnu = 0$.
From uniqueness of the Neumann problem in the exterior $E$, we conclude
that $\bu \equiv 0$ in $E$ as well, which in particular implies that
the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$.
Thus $(\cI - 2\cD_{k} - 2\cW)$ is invertible if $k$ is not a Dirichlet
eigenvalue for the Stokes equation on $\Omega$.

From Green's representation for the oscillatory Stokes qeuation, 
we know that 
  \begin{equation} \label{eq:rep-theorem}
    \bS_{k} [\bt](\xx) - \bD_{k}[\bu](\xx) = \begin{cases} 
    \bu(\xx) &\quad \xx \in \Omega \, , \\
    0 &\quad \xx \in \Omega^{C} \; .
    \end{cases}
  \end{equation}
Suppose that $k$ is Dirichlet eigenvalue for the Stokes equation on $\Omega$
and let $\bu$ denote the corresponding eigenfunction, and let $\bt^{-}$ denote
the surface traction associated with the eigenfunction on the boundary $\Gamma$.
Since $\bu$ is a Dirichlet eigenfunction, the velocity restricted to the boundary
$\bu^{-} = 0$. 
Applying the Green's theorem to the pair $\bt^{-}, \bu^{-}$ and taking 
its derivative on $\Gamma$ using~\cref{lem:jump-conds}, we get
\begin{equation}
\bt^{-} = (\cDt_{k} + \frac{1}{2} \cI) \bt^{-} \, ,\implies \left(\cI - 2\cDt_{k} \right) 
\bt^{-} = 0 \, .
\end{equation}
From the Fredholm alternative, it then follows that $(\cI - 2\cD_{k})$ has a non-trivial 
null-space.
However, we need to prove that $(\cI -2\cD_{k} - 2\cW)$ has a non-trivial null-space
for which we need the following two lemmas.

@@

\begin{lemma}
If $\bt^{-}$ is the surface traction associated with an interior Dirichlet
Stokes eigenfunction $\bu$, then $\bt^{-}$ and $\bnu$ are linearly independent.
\end{lemma}
\begin{proof}
We first note that $\bS_{k}[\bnu](\bx) = 0$ for all $\bx \in \Omega$.
This follows from the application of the divergence theorem and the fact that
oscillatory Stokeslet is divergence free in $\Omega$. 
If $\bt^{-}$ is a surface traction associated with a Stokes eigenvalue, then
using Green's theorem, it follows that
$\bS_{k}[\bt^{-}](\bx) = \bu(\bx) \neq 0$ for $\bx \in \Omega$ and
thus $\bt^{-}$ and $\bnu$ are linearly independent.
\end{proof}

We now return to the proof of~\cref{thm:dlmain}. 
We know that $\bt^{-}, \bnu \in \cN(\cI - 2\cDt_{k})$ are two linearly independent
vectors in the null space.
Let $c = \left< \bt^{-},\bnu \right>$. Then, it follows that 
$\left<\bt^{-} -c \bnu, \bnu \right> = 0$ and thus
$\cW[\bt^{-} - c\bnu] = 0$. 
Since $\bt^{-}$ and $\bnu$ are linearly independent, we note that
$\bt^{-} -c\bnu \neq 0$.
Combining these results, we get that
$(\cI - 2\cDt_{k} - 2\cW) (\bt^{-} - c\bnu) = 0$. 
Since $\bt^{-}-c\bnu$ is non-trivial, and $\cW$ is self-adjoint, 
it follows from the Fredholm alternative
that the operator $\cI - 2\cD_{k} - 2\cW$ is also not invertible.
\end{proof}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.3\linewidth]{media/multiply_final}
\end{center}
\caption{Example of a multiply connected domain with one obstacle.}
\label{fig:1ply}
\end{figure}

@@

As noted in~\cite{zhao2015robust}, this lack of one-to-one correspondance between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains causes non-robustness and introduces near 
resonanaces for simply connected domains
which are almost multiply connected.
We demonstrate this issue numerically in~\cref{sec:numanalysis-nearly-mult-con}.

\subsubsection{Mixed layer potential representation}
\label{subsec:mixedanalysis}
The non-robustness of the double layer potential representation
for computing the Dirichlet eigenvalues of Stokes equation can be remdied
by the standard approach of using the mixed layer potential representation,
i.e. setting
$\bu = (\bD_{k} + i\eta \bS_{k})
\bmu$, 
where $\bmu$ is the unknown density to be solved for, and $\eta \in \mathbb{R}^{+}$ 
On imposing the boundary conditions and using~\cref{lem:jump-conds}, 
we obtain the following integral equation on the boundary 
\begin{equation}
(\cI - 2\cD_{k} - 2i\eta \cS_{k}) \bmu = -2 \ff \, . 
\end{equation}
As noted in~\cref{subsubsec:nullspacecorr}, this integral equation 
is also rank-deficient, and we instead use the following 
equivalent integral equation for $\bmu$,
\begin{equation}
(\cI - 2\cD_{k} -2i\eta \cS_{k}  -2\cW)\bmu = -2 \ff \, .
\end{equation}

We now prove that for any bounded region $\Omega$ (simply or multiply
connected) with $C^{2}$ boundaries, there exists a one-to-one correspondance
between the invertibility of the operator
$\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$ and the Dirichlet eigenvalues
of the Stokes operator on $\Omega$.

\begin{thrm}
Suppose $\Omega$ is a bounded region defined by the intersection of a 
simply connected domain $\Omega_{0}$ and the exteriors of a finite collection
of bounded simply connected domains $\{ \Omega_{i} \}_{i=1}^{m}$.
As before let $\Gamma_{i}$ denote the boundary of $\Omega_{i}$ and let
$\Gamma = \cup_{i=0}^{m} \Gamma_{i}$ denote the boundary of $\Omega$.
Then the operator $\cI - 2\cD_{k} - 2i\eta \cS_{k} - 2\cW$
is invertible if and only if $k$ is not a Dirichlet eigenvalue
for the Stokes operator on $\Omega$.
\end{thrm}

\begin{proof}
Suppose that $k$ is not a Dirichlet eigenvalue for Stokes equation on
$\Omega$. 
Suppose further that $\bmu$ satisfies
\begin{equation}
(\cI - 2\cD_{k} -2i\eta\cS_{k} - 2\cW) \bmu = 0 \, , \label{eq:mlproofrep}
\end{equation}
i.e. $\bmu$ is in the null-space
of $(\cI - 2 \cD_{k} - 2i\eta \cS_{k} - 2 \cW)$. 
Applying the operator $\cW$ to~\cref{eq:mlproofrep} and 
using~\cref{lem:propnullspacecorr}, we get
\begin{equation}
0 = \cW [(\cI - 2\cD_{k} - 2i\eta\cS_{k} - 2\cW)\bmu] = -2\cW [\bmu] \, .
\end{equation}
Thus~\cref{eq:mlproofrep} reduces to
\begin{equation}
(\cI - 2 \cD_{k} - 2i\eta \cS_{k})\bmu = 0\, .
\end{equation}
Suppose now $\bu = -2\bD_{k}[\bmu] -2i\eta\bS_{k}[\bmu]$ in $\Omega$.
Then $\bu$ is a solution to the oscillatory Stokes equation in $\Omega$,
and applying~\cref{lem:jump-conds}, we get that the interior
limit of the velocity $\bu^{-} = (\cI - 2\cD_{k} -2i\eta\cS_{k}) \bmu = 0$ on $\Gamma$. 
Since $k$ is not a Dirichlet eigenvalue for the Stokes equation on 
$\Omega$, we conclude that $\bu \equiv 0$ in $\Omega$. 
This in particular implies that the interior limit of the surface traction
denoted by $\bt^{-} = 0$ on $\Gamma$.
Using~\cref{lem:jump-conds}  
we observe that the exterior limit 
of the surface traction is $\bt^{+} = i\eta \bmu(\xx)$
and the exterior limit of the velocity is 
$\bu^{+} = \bmu(\xx)$ on $\Gamma$.
\begin{remark}
Note that there is a slight abuse of notation here for the obstacle
boundaries, since the exterior limit with respect to $\Omega$ 
for the boundary $\Gamma_{j}$ is the traditional interior 
limit with respect to the obstacle region $\Omega_{j}$.
\end{remark}
We first show that $\bmu=0$ on $\Gamma_{0}$. 
To this end, note that $\bu$ is a radiating solution of the oscillatory
Stokes equation in the exterior $E$,
since $\cW[\bmu] = 0$ implies that $\int_{\Gamma} \bmu \cdot \bnu = 0$. 
From uniqueness of the impedance problem in the exterior $E$, we conclude
that $\bu \equiv 0$ in $E$ as well, which in particular implies that
the exterior limit of the velocity $\bu^{+}=0$ on $\Gamma_{0}$.   
Using the jump conditions in~\cref{lem:jump-conds} again, we
get that $\bmu = \frac{1}{2}(\bu^{+} - \bu^{-}) = 0$ \, on
$\Gamma_{0}$. 
To show that $\bmu=0$ on $\Gamma_{j}$, we observe that
$\bmu$ is also a solution to the oscillatory Stokes equation
in each of the obstacles $\Omega_{j}$ as well.
Applying Green's identity and using the fact that 
the interior limits with respect to $\Omega_{j}$ (see remark)
of the surface traction and the velocity
are $i\eta \bmu$ and $\bmu$ respectively, we get
\begin{equation}
\int_{\Omega_{j}} (|e(\bu)|^{2} - \overline{k}^{2} |\bu|^2) dV 
= \int_{\Gamma_{j}} \bu \cdot \overline{\bt} dS = 
i\overline{\eta}\int_{\Gamma_{j}} |\bmu|^2 dS \, .
\end{equation}
Taking the imaginary part of the above equation, we get
\begin{equation}
2 \text{Re}(k) \text{Im}(k) \int_{\Omega_{j}} |\bu|^2 + \text{Re}(\eta)
\int_{\Gamma_{j}} |\bmu|^2 dS = 0 \, .
\end{equation}
Since $\text{Re}(\eta)>0$, this implies that $\bmu=0$ for $\xx \in \Gamma_{j}$, $j=1,2,\ldots m$. 
Thus $\cI - 2\cD_{k} -2i\eta\cS_{k} -2\cW$ is invertible when $k$ 
is not a Dirichlet eigenvalue for the Stokes equation on $\Omega$.
